14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-11 rules/rules19.tex
Rules: Update list of changes (+ TODOs).
+ changes: update time limit section

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
\todo{update changes vs 2018}
The principal changes from the previous competition rules are the following:
\begin{itemize}
\item The time limit per solver/benchmark pair is anticipated to be at
  most 20 minutes in the \main Track, and at most 40 minutes in the
  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
  the \main Track was reduced to 20 minutes (down from 40 minutes in
  earlier years) to cope with the inclusion of a large number of
  benchmarks with unknown status.

\item In the \ucore Track, the unsatisfiability check for the
  returned core will be based on a simple majority vote.  The case
  that a solver finds its own core satisfiable will no longer be
  treated specially.  \emph{Rationale:} This allows to simplify the
  post-processing of \ucore Track results considerably.

\item In 2017, the competition featured experimental divisions for
  benchmarks that use algebraic datatypes.  These divisions will be
  regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
  datatypes are specified in the latest official release (Version~2.6)
  of the SMT-LIB standard.

\item The competition will feature an experimental divisions for
  benchmarks that use strings.  \emph{Rationale:} Corresponding
  theories and benchmarks are expected to be added to SMT-LIB in the
  near future.
\end{itemize}

@@

The \challenge Track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on
all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
 \emph{industrial}. Additionally we will include benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
know if the problem is sat/unsat}

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\it Renaming of Tracks.} \todo{}

  \item {\it Mandatory System Descriptions.} \todo{}

  \item {\it Do Not Run Non-Competitive Divisions.} \todo{}

  \item {\it Benchmark Selection.} \todo{}

  \item {\it Time Limit.} The time limit per solver/benchmark pair is
    anticipated to be at most 40 minutes in the \main (formerly: Main),
    \incremental (formerly: Application), \ucore and \mval Tracks.  For the
    \challenge Track, it is anticipated to be at most \todo{xx} minutes.
    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
    the inclusion of a large number of benchmarks with unknown status.  This
    year, the reduced number of benchmarks selected per division allows us to
    increase the time limit back to 40 minutes for the \main Track.

  \item {\it New \mval Track.} \todo{}

  \item {\it New \challenge Track.} \todo{}
.
  \item {\it New Scores.} \todo{24 seconds, sat, unsat}

  \item {\it Incremental Track.} \todo{Run beyond the first unknown status query}

  \item {\it Experimental Strings Division.}
    \todo{point to the current draft of the standard as the set of rules
    solvers have to agree on}
    The competition will feature an experimental divisions for
  benchmarks that use strings.  \emph{Rationale:} Corresponding
  theories and benchmarks are expected to be added to SMT-LIB in the
  near future.

  \item {\it Scoring Scheme.} \todo{}

  \item {\it Competition-Wide Scores/Winners.} \todo{}

  \item {\it Problems with Evaluation Scripts.} \todo{Explain what was the
    problem and what has been fixed, talk about notion of benchmark family.}

\end{itemize}

@@

\todo{time limit}
The \challenge Track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on
all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
 \emph{industrial}. Additionally we will include benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
know if the problem is sat/unsat}
